---
title: "Supermart Sales Analysis"
author: "Chloe Shin"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.align = "center")
knitr::opts_chunk$set(message = FALSE)
set.seed(0)
```

## Data Preparation
```{r}
library(tidyverse)
library(tidymodels)
library(knitr)
ifood <- read_csv("https://raw.githubusercontent.com/nailson/ifood-data-business-analyst-test/refs/heads/master/ifood_df.csv")
```

```{r}
ifood <- ifood %>% 
  distinct()
```

## Customer Profile 

### 1. Age Distribution
```{r}
ifood %>% 
  ggplot(aes(x = Age)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), 
                 binwidth = 5, 
                 fill = 'orange') +
  labs(x = "Age", 
       y = "Proportion", 
       title = "Age Distribution") +
  theme_minimal() +
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15))
  )
```

### 2. Income Distribution
```{r}
ifood %>% 
  ggplot(aes(x = Income)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count))), 
                 binwidth = 10000, 
                 fill = 'skyblue') +
  labs(x = "Annual Income (USD)", 
       y = "Proportion", 
       title = "Income Distribution") +
  theme_minimal() +
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15))
  )
```

### 3. Marital Status
```{r}
ifood_marriage <- ifood %>%
  pivot_longer(cols = c(marital_Widow, 
                        marital_Divorced, 
                        marital_Together, 
                        marital_Single, 
                        marital_Married),
               names_to = 'marital',
               values_to = 'value') %>%
  filter(value == 1)

ifood_marriage <- ifood_marriage %>%
  mutate (marital = recode(marital,
      marital_Divorced = "Divorced",
      marital_Married  = "Married",
      marital_Single   = "Single",
      marital_Together = "Together",
      marital_Widow    = "Widow")) %>%
  mutate(proportion = value / sum(value))
```

```{r}
ifood_marriage %>%
  ggplot(aes(x = marital, 
             y = proportion, 
             fill = marital)) +
  geom_col(fill = 'lightgreen') +
  labs (x = 'Marital Status', 
        y = 'Proportion', 
        title = 'Marital Status Distribution') +
  theme_minimal() +
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15))
  )
```

### 4. Highest Education
```{r}
ifood_education <- ifood %>%
   pivot_longer(cols = c(`education_2n Cycle`, 
                         education_Basic, 
                         education_Graduation, 
                         education_Master, 
                         education_PhD ),
               names_to = 'education',
               values_to = 'value') %>%
  filter(value == 1)

ifood_education <- ifood_education %>%
  mutate (education = recode(education,
      `education_2n Cycle` = "2n Cycle",
      education_Basic  = "Basic",
      education_Graduation   = "Bachelor",
      education_Master = "Master",
      education_PhD    = "PhD")) %>%
      mutate(proportion = value / sum(value))
```

```{r}
ifood_education %>%
  mutate(education = factor(education, 
                            levels = c("Basic", "2n Cycle","Bachelor", "Master", "PhD"))) %>%
  ggplot(aes(x = education, 
             y = proportion, 
             fill = education)) +
  geom_col(fill = 'yellow') +
  labs (x = 'Highest Education', 
        y = 'Proportion', 
        title = 'Education Status Distribution') +  
  theme_minimal() +
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15))
  )
```

## Previous Campaigns Acceptance Rate
```{r}
ifood_campaign <- ifood[, c("AcceptedCmp1", 
                            "AcceptedCmp2", 
                            "AcceptedCmp3", 
                            "AcceptedCmp4", 
                            "AcceptedCmp5", 
                            "Response")]

ifood_campaign <- ifood %>% 
  summarise("Campaign 1" = sum(AcceptedCmp1),
         "Campaign 2" = sum(AcceptedCmp2), 
         "Campaign 3" = sum(AcceptedCmp3),
         "Campaign 4" = sum(AcceptedCmp4),
         "Campaign 5" = sum(AcceptedCmp5), 
         "Current Campaign" = sum(Response)) %>%
    pivot_longer(cols = everything(),
               names_to = "campaign",
               values_to = "value") %>%
    mutate(proportion = value / sum(value))
```

```{r}
ifood_campaign %>%
  ggplot(aes(x = campaign,
             y = proportion)) +
  geom_col(fill = "purple") +
  coord_flip() +
  labs(
    x = "Campaign",
    y = "Proportion Accepted",
    title = "Campaign Acceptance Rates"
  ) + 
  theme_minimal() +
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15))
  )
```

## Effect of Previous Campaign Engagement

### 1. Previous Any
```{r}
ifood_acceptcmp <- ifood %>%
  select(AcceptedCmp1, AcceptedCmp2, AcceptedCmp3, AcceptedCmp4, AcceptedCmp5, Response) %>%
  mutate(numaccept = rowSums(select(., AcceptedCmp1:AcceptedCmp5)), 
         prevaccept = numaccept > 0)
```

```{r}
prop.table(table(ifood_acceptcmp$prevaccept, ifood_acceptcmp$Response), 1)
chisq.test(table(ifood_acceptcmp$prevaccept, ifood_acceptcmp$Response))
```

Among the customers who did not accept any of the previous campaigns, only 8.35% accepted the current campaign. On the other hand, among the customers who accepted at least one of the previous campaigns, 40.8% accepted the current campaign.   

Previous engagement with campaigns significantly increases the likelihood of responding to the current campaign. 

### 2. Most Recent
```{r}
prop.table(table(ifood_acceptcmp$AcceptedCmp5, ifood_acceptcmp$Response), 1)
chisq.test(table(ifood_acceptcmp$AcceptedCmp5, ifood_acceptcmp$Response))
```
Among the customers who did not the most recent campaign, 11.84% accepted the current campaign. On the other hand, among the customers who accepted the most recent campaign, 56.52% accepted the current campaign. 

Engagement with the most recent campign significantly increases the likelihood of responding to the current campaign.  